---
title: "graphs"
author: "Helen Yuan -- 106145727"
date: "`r Sys.Date()`"
output: html_document
---

# Load stuff
```{r}
library(stringr)
library(lubridate)
library(hms)
library(ggplot2)
library(dplyr)
library(randomForest)
library(corrplot)

setwd("~/Downloads/datafest/Random Sample of Data Files")
big <- read.csv("big.csv")
```

# EOC as students progress through the books
In general students' EOC scores get lower and lower as they progress through the 
book. Each colored line represents one student.

> levels(big$book)
[1] "College / Advanced Statistics and Data Science (ABCD)"     
[2] "College / Statistics and Data Science (ABC)"               
[3] "High School / Advanced Statistics and Data Science I (ABC)"

```{r}
big |> ggplot(aes(x = ratio_correct, color = institution_id)) +
  geom_boxplot()
# Convert book column to factor
big$book <- factor(big$book)
big |> ggplot(aes(x = chapter_number, y = ratio_correct), group = student_id) +
  geom_point(aes(color = student_id), show.legend = FALSE) +
  geom_line(aes(color = student_id), show.legend = FALSE) # this is too cluttered

big[as.numeric(big$book) == 1,] |> 
  ggplot(aes(x = chapter_number, y = ratio_correct), group = student_id) +
  geom_point(aes(color = student_id), show.legend = FALSE, alpha = 0.5) +
  geom_line(aes(color = student_id), show.legend = FALSE, alpha = 0.5) 

big |> group_by(book, chapter_number) |> summarize(ratio_correct = mean(ratio_correct, na.rm = TRUE)) |> ggplot(aes(x = chapter_number, y = ratio_correct, color = book)) +
  geom_point(cex = 3) +
  geom_line()
```
# Why are high schoolers scoring so low?
Seems like they don't differ too much in time engaged/idle/off page or anything
actually maybe they're just stupid

```{r}
# Remove outliers 
big[big$n_attempt < 300,] |> group_by(book, student_id) |> summarize(n_attempt = mean(n_attempt, na.rm = TRUE), ratio_correct = mean(ratio_correct, na.rm = TRUE)) |> 
  ggplot(aes(x = n_attempt, color = book)) +
  geom_boxplot() +
  theme(legend.position = "bottom")
```
Are students who start out struggling still struggling?

```{r}
big |> pivot_wider(id_cols = c(student_id), names_from = chapter_number, values_from = ratio_correct) |> 
  ggplot(aes(x = `4`, y = `10`)) +
  geom_point() # etc...
```
# Insights from media views
```{r}
big |> ggplot(aes(x = proportion_video, y = ratio_correct)) + 
  geom_point(aes(color = book)) +
  theme()
pairs(~ratio_correct+off_page_long+idle_long+engaged, big)
big[big$off_page_long < 1e+07,] |> ggplot(aes(x = off_page_long, y = ratio_correct)) +
  geom_point(alpha = 0.25)

# As chapters go on...
big |> mutate(on_task_ratio = engaged/(off_page_brief+off_page_long)) |> 
  filter(on_task_ratio < 3.318226) |> 
  ggplot(aes(x = on_task_ratio, y = ratio_correct)) +
  geom_point(aes(color = institution_id))

summary(big$engaged/(big$off_page_brief+big$off_page_long)) # outliers at 3.318226
```
