---
title: "graphs"
author: "Helen Yuan -- 106145727"
date: "`r Sys.Date()`"
output: html_document
---

# Load stuff
```{r}
library(stringr)
library(lubridate)
library(hms)
library(ggplot2)
library(dplyr)
library(randomForest)
library(corrplot)

setwd("~/Downloads/datafest/Random Sample of Data Files")
page_views <- read.csv("page_views.csv")
media_views <- read.csv("media_views.csv")
items <- read.csv("items.csv")
responses <- read.csv("responses.csv")
pulse <- read.csv("checkpoints_pulse.csv")
eoc <- read.csv("checkpoints_eoc.csv")
codebook <- read.csv("../Documentation/codebook.csv")
variable_list <- read.csv("../Documentation/variable_list.csv")
```

# Some inner joins
I used a subset consisting of only one book
```{r}
eoc_abcd <- eoc[eoc$book == "College / Advanced Statistics and Data Science (ABCD)",]
pulse_abcd <- pulse[pulse$book == "College / Advanced Statistics and Data Science (ABCD)",]
joined <- pulse_abcd |> na.omit() |> 
  pivot_wider(names_from = construct, values_from = response, values_fn = mean) |> 
  inner_join(select(eoc_abcd, student_id, chapter_number, EOC))
```

# Some graphs
This one's really messy and hard to read, but it shows that in general students' 
EOC scores get lower and lower as they progress through the book. Each colored 
line represents one student.
```{r}
eoc_abcd |> ggplot(aes(x = chapter_number, y = EOC, group = student_id)) +
  geom_point(aes(color = student_id), show.legend = FALSE) + 
  geom_line(aes(color = student_id), alpha = 0.5, show.legend = FALSE)
```
I grouped the chapters into "early" (1-4), "middle" (5-12) and "late" (13-16). I
also summarized students' average EOC scores within each phase and graphed each
students' average "early" phase EOC scores against their "late" phase scores.
Seems like students who are struggling in the beginning are still struggling
by the end?
```{r}
eoc_abcd$phase <- ifelse(eoc_abcd$chapter_number < 5, "early", ifelse(eoc_abcd$chapter_number > 12, "late", "middle"))
eoc_abcd |> group_by(student_id, phase) |> summarize(EOC = mean(EOC, na.rm = TRUE)) |> 
  pivot_wider(names_from = phase, values_from = EOC) |> 
  ggplot(aes(x = early, y = late)) +
  geom_point()
```
